Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-05 Tex/Paper.tex
Updates
Added line endings

% ************************************************************************************************ %
\begin{document}
% ************************************************************************************************ %

@@

The preliminary design of AWAKE Run 2 will split the plasma cell into two sections. The first section of 4m is the SMI stage. The electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the $e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible \cite{adli:2016}.

@@

% ************************************************************************************************ %
\end{document}
% ************************************************************************************************ %

>>>>

% ******************************************************************************************************************** %
\begin{document}
% ******************************************************************************************************************** %

@@

The preliminary design of AWAKE Run 2 proposes to use two plasma sections. The first section of 4m is the SMI stage. The
electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
$e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible
\cite{adli:2016}.

@@

% ******************************************************************************************************************** %
\end{document}
% ******************************************************************************************************************** %
